Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-09 prop.tex
prop.tex \section{Introduction} Add citations, but it's delicate whether these citations fit here or not...

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and computations
are processes bounded in space, time, energy, and other resources.
Yet, for centuries, the mathematical formalization of such processes
has been founded on the infinitely precise real or complex numbers~\cite{Kent1999,CliftonKent2000}.
Indeed, almost every description of quantum mechanics, quantum computation,
or quantum experiments refers to entities such as $e$, $\pi$, $\sqrt{2}$,
etc. From a computational perspective, such numbers do not exist in
their entirety ``for free.'' For example, the state of the art algorithms
for computing the $n$th binary digit of~$\pi$ require on the order
of $O(n\log^{O(1)}(n))$ operations~\cite{journals/moc/BaileyBP97}.
In other words, simply referring to the $n$th digit of $\pi$ requires
more and more resources as $n$ gets larger. Taking such resource
bounds into consideration is what founded computer science as a discipline
and is crucial for understanding the very nature of computation and,
following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, for understanding the very nature of physical processes.

>>>>

This is a \emph{theoretical} investigation of \emph{experimental}
physics using \emph{computational} methods. All experiments and computations
are processes bounded in space, time, energy, and other resources~\cite{Jaeger2007,Li2009}.
Yet, for centuries, the mathematical formalization of such processes
has been founded on the infinitely precise real or complex numbers~\cite{Kent1999,CliftonKent2000}.
Indeed, almost every description of quantum mechanics, quantum computation,
or quantum experiments refers to entities such as $\rme$, $\pi$,
$\sqrt{2}$, etc. From a computational perspective, such numbers do
not exist in their entirety ``for free.'' For example, the state
of the art algorithms for computing the $n$th binary digit of~$\pi$
require on the order of $O(n\log^{O(1)}(n))$ operations~\cite{journals/moc/BaileyBP97}.
In other words, simply referring to the $n$th digit of $\pi$ requires
more and more resources as $n$ gets larger. Taking such resource
bounds into consideration is what founded computer science as a discipline
and is crucial for understanding the very nature of computation and,
following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, for understanding the very nature of physical processes.
